Acceleration of Global Search by Implementing Dual Estimates for Lipschitz Constant\thanks{This research was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-09-09 2019/NUMTA_Barkalov/LNCS/numta19.tex
Fix some mistakes

\begin{document}
%
\title{Acceleration of Global Search by Implementing Dual Estimates for Lipschitz Constant\thanks{This research was supported by the the Russian Science Foundation, project No.\,16-11-10150.}}
%
\titlerunning{Acceleration of Global Search}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Roman Strongin\orcidID{0000-0003-0390-6695} 
\and Konstantin Barkalov\orcidID{0000-0001-5273-2471} 
\and Semen Bevzuk\orcidID{0000-0002-3845-5356}
}
%
\authorrunning{R. Strongin et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia
\email{konstantin.barkalov@itmm.unn.ru}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The paper considers global optimization problems with a black-box objective 
function satisfying the Lipschitz condition. Efficient algorithms for this 
class of problems require reliable estimates of the Lipschitz constant to be 
introduced. The various approaches have been proposed to take into account both
global and local properties of the objective function. In particular, algorithms
using local estimates of the Lipschitz constant have shown their potential.
The new approach presented in this paper is based on simultaneous use of two
estimates: one is substantially larger than the other. 
The larger estimate ensures global convergence and the smaller one reduces 
the total number of trials needed to find the global optimizer.
Results of numerical experiments on the random sample of multidimensional 
functions demonstrate the efficiency of the suggested approach.

@@

The assumption of the objective function to be Lipschitzian is typical for many approaches to the development of the global optimization algorithms \cite{Evtushenko2013,Zilinskas2010,Pinter1996,Strongin2000}. Moreover, the adaptive estimate of the unknown Lipschitz constant, based on the obtained search information, is one of the most important problems being solved in these algorithms. 
The value of the Lipschitz constant affects the convergence rate of the global optimization algorithms essentially. Therefore, the issue of its correct estimate is so important. 
The underestimation of the real value of this constant may result in losing the convergence of the algorithm to the global solution. At the same time, a too large value of the estimate of the constant could bring the objective function not matching its real behavior. This produces slow convergence of the algorithm to the global minimizer.

@@

Each approach from the above has its own advantages and disadvantages. For example, the use of the global estimate over the whole search domain can slow down the convergence of the algorithm to the global minimizer. The use of the local estimates to accelerate the convergence of the method requires an adequate adjustment of the parameters of the algorithm in order to preserve the global convergence.

In the present work, it is considered a new algorithm in which there is the use of two global estimates of the Lipschitz constant. One of the two estimates is much greater than the other one. 
The larger estimate ensures global convergence and the smaller one reduces the total number of trials needed to find the global optimizer.
The choice of one of the two estimates in the algorithm is performed adaptively during the search phase.

The rigorous substantiation of the proposed approach goes beyond the present initial publication and will be done in the forthcoming works. Here we present the results of numerical experiments that clearly demonstrate the efficiency of the new algorithm. Several hundred multiextremal test problems of various dimensionalities have been solved conducting numerical experiments.

@@

In the present paper, the approach based on the ideas of reduction of dimension with the use of the Peano-Hilbert curves \cite{Sergeyev2013,Strongin2000}, which continuously and unambiguously maps the unit interval $[0,1]$ onto the $N$-dimensional cube $D$ from (\ref{D}) has been used. By using this kind of mapping, it is possible to reduce the multidimensional problem (\ref{problem}) to a univariate problem
\[
\varphi(y^\ast)=\varphi(y(x^\ast))=\min{\left\{\varphi(y(x)): x\in[0,1]\right\}},
\]
where the function $\varphi(y(x))$ will satisfy a uniform H{\"o}lder condition
\[
\left|\varphi(y(x_1))-\varphi(y(x_2))\right|\leq H\left|x_1-x_2\right|^{1/N},
\]
with the H{\"o}lder constant $H$ linked to the Lipschitz constant $L$ by the relation
$ H=2 L \sqrt{N+3}$ and $y(x)$ is a Peano-Hilbert curve from $[0,1]$ onto $D$.
%Russian
Отметим, что теоретически Peano-Hilbert curve $y(x)$ определяется as a limit object. Поэтому при практической реализации может быть построено лишь некоторое приближение к истинной space-filling curve. Методы построения подобных approximations (называемых evolvents) рассмотрены в \cite{Sergeyev2013,Strongin2000}. При этом точность приближения развертки к истинной кривой $y(x)$ зависит от плотности развертки $m$ (являющейся параметром ее построения) и составляет величину порядка $2^{-m}$ по каждой координате.

@@

The global search algorithm presented in previous section is intended for solving the multiextremal problems, in which the objective function satisfies the Lipschitz condition. It is not necessary to define the value of the constant for the algorithm convergence. The estimation of the constant is performed in the course of global search on the base of available search information. 
According to the theorem from \cite{Strongin2000}, the sequence of the trial points $\{y^k\}$ will converge to the global minimizer $y^*$ if the condition 
\begin{equation}\label{cond}
r\mu > 2^{3-1/N}L\sqrt{N+3}.
\end{equation}
\noindent is satisfied. Thus,  an appropriate choice of the parameter $r$ from (\ref{R}) allows using the value $(r\mu) / (2^{3-1/N}\sqrt{N+3})$ as an estimate of the Lipschitz constant for the objective function $\varphi(y)$.

Satisfying the condition (\ref{cond}) will be guaranteed at choosing large enough value of the parameter $r$. However, in this case the method will perform a large number of trials until the stop condition is satisfied.
The choice of a small value of the parameter $r$ (that corresponds to the lower estimate of the Lipschitz constant) would considerably reduce the number of trials but may violate the convergence to the global extremum.

An approach, in which two estimates of the Lipschitz constant %, one of which is essentially greater than another, 
are used in the rules of the algorithm, is a promising one. 
This approach implies the use of two parameters $r_{glob}$ and $r_{loc}$ where $r_{glob} > r_{loc}>1$ in the algorithm.

%Russian
The rules of the algorithm with two estimates of the Lipschitz constant reproduce the ones of global search algorithm completely except Rule 3 (the computation of the characteristic) and Rule 4 (поиск интервала с максимальной характеристикой).

New rule of calculating the characteristic $R(i)$ of the interval $(x_{i-1}, x_i)$ will consist of the following operations:
\begin{itemize}
\item
Calculate the value $R_{glob}(i)$ corresponding to the larger estimate of the Lipschitz constant
\[
R_{glob}(i)=\Delta_i+\frac{(z_i-z_{i-1})^2}{r_{glob}^2\mu^2\Delta_i}-2\frac{z_i+z_{i-1}-2z^*}{r_{glob}\mu}.
\]
\item
Calculate the value $R_{loc}(i)$ corresponding to the smaller estimate of the Lipschitz constant
\[
R_{loc}(i)=\Delta_i+\frac{(z_i-z_{i-1})^2}{r_{loc}^2\mu^2\Delta_i}-2\frac{z_i+z_{i-1}-2z^*}{r_{loc}\mu}.
\]
\item
Determine the characteristic $R(i)$ as
\begin{equation}\label{pho}
R(i) = \max\{\rho R_{loc}(i),R_{glob}(i)\}, \textrm{where} \; \rho = \left(\frac{1-1/r_{glob}}{1-1/r_{loc}}\right)^2,
\end{equation}   
\end{itemize}

%Russian
Новые правила поиска интервала с максимальной характеристикой будут состоять в следующем:
\begin{itemize}
\item 
Select the interval $(x_{t-1},x_t)$ corresponding to the maximum characteristic
\[
R(t)= \max_{1 \leq i \leq k}R(i).
\]
\item
Fix the value $r = r_{loc}$ if $\rho R_{loc}(t) > R_{glob}(t)$, otherwise fix $r=r_{glob}$.
\item
This value of $r$ is used in Rule 5 of the algorithm in the computing of the next trial point.
\end{itemize}

This method of computing the characteristic is substantiated as follows. 
%Russian
На каждой итерации будет возникать интервал, на одной из границ которого достигается текущее минимальное значение $z^*$ from (\ref{z}). Причем на заключительной фазе поиска данный интервал будет соответствовать интервалу, содержащему глобальный минимум, т.е. будет являться лучшим с точки зрения проведения дальнейших испытаний в нем.

Let current minimum value of $z^*$ from (\ref{z}) be achieved at the left point of the $i^{\rm th}$ interval, i.e. $z^* = z_{i-1}$. Then, according to the rule (\ref{R}) the following inequality will be true: 
\[
R(i) \geq \Delta_i \left( 1 - \frac{1}{r} \right)^2.
\]
Следовательно, для нижних оценок характеристик $R_{loc}(i)$ and $R_{glob}(i)$ calculated with different parameters $r_{loc}$ and $r_{glob}$, будет выполняться соотношение
\[
	\Delta_i \left( 1 - \frac{1}{r_{glob}} \right)^2 > \Delta_i \left( 1 - \frac{1}{r_{loc}} \right)^2.
\]

Таким образом, если выбирать наибольую из характеристик в соответствии с
\[
R(i) = \max\{R_{loc}(i),R_{glob}(i)\}
\]
то, как правило, будет выбираться характеристика $R_{glob}(i)$, соответствующая большей оценке Lipschitz constant; меньшая оценка (ускоряющая процесс уточнения текущего решения) использоваться не будет.
Однако если домножить нижнюю оценку для характеристики $R_{loc}(i)$ на коэффициент $\rho$ в соответствии с (\ref{pho}), то указанные нижние оценки будут равны, что сделает более вероятным выбор характеристики $R_{loc}(i)$, соответствующей меньшей оценке Lipschitz constant.

@@

%Russian
Численное сравление алгоритмов было выполнено посредством решения нескольких серий задач, порожденных генератором GKLS \cite{Gaviano2003}. Данный генератор of multiextremal functions широко используется для сравнения методов глобальной оптимизации (see, for example, \cite{Barkalov2018,Paulavicius2014,Sergeyev2015}). В данном исследовании были решены шесть серий по 100 задач размерностей $N = 3,4,5$. Для каждой размерности генерировались \textit{Simple} and \textit{Hard} problems, отличающиеся размерами attraction region локальных и глобального экстремума.
Задача считалась решенной, если метод проводил очередное испытание в точке $y^k$, которая находилась в $\delta$-октрестности global minimizer $y^\ast$, 
т.е. $\left\|y^k-y^\ast\right\| <\delta\left\|b-a\right\|$, where  $a$ and $b$ --- границы search domain $D$.

@@

The averaged numbers of iterations performed by the algorithms are presented in Table \ref{tab:1}.
At that, for GSA the values of parameter $r=4.8$ when solving the problems of Simple class and $r=5.6$ when solving the problems of Hard class were used. 
These values are the minimum ones (with the accuracy 0.1), at which all problems have been solved successfully.
When solving the problems from the above classes by GSA-DL, the value of parameter $r$ specified above was selected for the upper estimate of the Lipschitz constant, i.e. the value $r_{glob} = r$ was set, which was complemented by the values $r_{loc}=1.8$, $r_{loc}=2.1$ and $r_{loc}=2.4$. 
The number of unsolved problems is specified in brackets.

@@

The advantage of the GSA-DL algorithm over its prototype is confirmed by the operational characteristics of the algorithms as well.

@@

The operational characteristics for the GSA and GSA-DL methods obtained when solving the \textit{Simple} and \textit{Hard} problem series with the dimensionalities $N=4$ and $N=5$ are presented in Fig. \ref{oper4} and \ref{oper5}, respectively. The values of the parameters $r$ used for estimating the Lipschitz constant are given in the figures.

The lower curves in Fig. \ref{oper4} and \ref{oper5} feature GSA whereas the upper ones --- GSA-DL. Such positions of the curves show the algorithm with two estimates of the Lipschitz constant provides much faster solving of the problem series in average that the algorithm using single estimate of the constant.
%Russian
Отметим, что для решения задач всех классов (кроме класса  \textit{Hard} при $N=5$) метод GSA-DL требует примерно в два раза меньше испытаний, чем GSA. Ухудшение результатов на классе \textit{Hard} при $N=5$ объясняется сложностью функций данного класса, характеризующихся большими attraction region локальных минимумов и узкой attraction region глобального минимума. Для корректного решения таких задач метод  GSA-DL чаще использует бОльшую оценку константы Липшица, что сближает скорость работы алгоритмов GSA и GSA-DL.

>>>>

\begin{document}
%
\title{Acceleration of Global Search by Implementing Dual Estimates for Lipschitz Constant\thanks{This research was supported by the Russian Science Foundation, project No.\,16-11-10150.}}
%
\titlerunning{Acceleration of Global Search}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Roman Strongin\orcidID{0000-0003-0390-6695} 
\and Konstantin Barkalov\orcidID{0000-0001-5273-2471} 
\and Semen Bevzuk\orcidID{0000-0002-3845-5356}
}
%
\authorrunning{R. Strongin et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia
\email{konstantin.barkalov@itmm.unn.ru}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The paper considers global optimization problems with a black-box objective 
function satisfying the Lipschitz condition. Efficient algorithms for this 
class of problems require reliable estimates of the Lipschitz constant to be 
introduced. Various approaches have been proposed to take into account both
global and local properties of the objective function. In particular, algorithms
using local estimates of the Lipschitz constant have shown their potential.
The new approach presented in this paper is based on simultaneous use of two
estimates: one is substantially larger than the other. 
The larger estimate ensures global convergence and the smaller one reduces 
the total number of trials needed to find the global optimizer.
Results of numerical experiments on the random sample of multidimensional 
functions demonstrate the efficiency of the approach proposed by the authors.

@@

The assumption of the objective function to be Lipschitzian is typical of many approaches to the development of the global optimization algorithms \cite{Evtushenko2013,Zilinskas2010,Pinter1996,Strongin2000}. Moreover, the adaptive estimate of the unknown Lipschitz constant, based on the obtained search information, is one of the most important problems being solved in these algorithms. 
The value of the Lipschitz constant affects essentially the convergence rate of the global optimization algorithms. Therefore, the issue of its correct estimate is so important. 
The underestimation of the real value of this constant may result in losing the convergence of the algorithm to the global solution. At the same time, if the value of the constant estimate is too large, the objective function may not match its real behavior. This results in  slow convergence of the algorithm to the global minimizer.

@@

Each of the above approaches has its own advantages and disadvantages. For example, the use of the global estimate over the whole search domain can slow down the convergence of the algorithm to the global minimizer. The use of the local estimates to accelerate the convergence of the method requires an adequate adjustment of the algorithm parameters in order to preserve the global convergence.

In the present work, we  consider a new algorithm that uses two global estimates of the Lipschitz constant. One of the two estimates is much greater than the other one. 
The larger estimate ensures global convergence and the smaller one reduces the total number of trials needed to find the global optimizer.
The choice of one of the two estimates in the algorithm is performed adaptively during the search phase.

A rigorous substantiation of the proposed approach goes beyond the present initial publication and will be done in the forthcoming works. Here we present the results of numerical experiments that clearly demonstrate the efficiency of the new algorithm. Several hundred multiextremal test problems of various dimensionalities have been solved in the course of numerical experiments.

@@

In this paper, we follow the approach based on the idea of reducing the dimension with the use of the Peano-Hilbert curves \cite{Sergeyev2013,Strongin2000}, which continuously and unambiguously map the unit interval $[0,1]$ onto the $N$-dimensional cube $D$ from (\ref{D}) has been used. By using this kind of mapping, it is possible to reduce the multidimensional problem (\ref{problem}) to a univariate problem
\[
\varphi(y^\ast)=\varphi(y(x^\ast))=\min{\left\{\varphi(y(x)): x\in[0,1]\right\}},
\]
where the function $\varphi(y(x))$ will satisfy a uniform H{\"o}lder condition
\[
\left|\varphi(y(x_1))-\varphi(y(x_2))\right|\leq H\left|x_1-x_2\right|^{1/N},
\]
with the H{\"o}lder constant $H$ linked to the Lipschitz constant $L$ by the relation
$ H=2 L \sqrt{N+3}$ and $y(x)$ is a Peano-Hilbert curve from $[0,1]$ onto $D$.
%Russian
Note that theoretically the Peano-Hilbert curve $y(x)$ определяется as a limit object. is defined as a limit object. Therefore, in practical implementation, only some approximation to the true space-filling curve can be constructed. Some methods for constructing this type of approximations (called evolvents) are considered in \cite{Sergeyev2013,Strongin2000}. При этом точность приближения развертки к истинной кривой $y(x)$ зависит от плотности развертки $m$ (являющейся параметром ее построения) и составляет величину порядка $2^{-m}$ по каждой координате.

@@

The global search algorithm presented in the previous section is intended for solving the multiextremal problems, in which the objective function satisfies the Lipschitz condition. It is not necessary to define the value of the constant for the algorithm convergence. The estimation of the constant is performed in the course of global search based on available search information. 
According to the theorem from \cite{Strongin2000}, the sequence of the trial points $\{y^k\}$ will converge to the global minimizer $y^*$ if the condition 
\begin{equation}\label{cond}
r\mu > 2^{3-1/N}L\sqrt{N+3}.
\end{equation}
\noindent is satisfied. Thus,  an appropriate choice of the parameter $r$ from (\ref{R}) allows using the value $(r\mu) / (2^{3-1/N}\sqrt{N+3})$ as an estimate of the Lipschitz constant for the objective function $\varphi(y)$.

Satisfying the condition (\ref{cond}) will be guaranteed if we choose a large enough value of the parameter $r$. However, in this case the method will perform a large number of trials until the stop condition is satisfied.
The choice of a small value of the parameter $r$ (that corresponds to the lower estimate of the Lipschitz constant) would considerably reduce the number of trials but may violate the convergence to the global extremum.

An approach, in which two estimates of the Lipschitz constant %, one of which is essentially greater than another, 
are used in the rules of the algorithm, seems quite promising. 
This approach implies the use in the algorithm of two parameters $r_{glob}$ and $r_{loc}$ where $r_{glob} > r_{loc}>1$.

%Russian
The rules of the algorithm with two estimates of the Lipschitz constant reproduce the ones of the global search algorithm completely except Rule 3 (the computation of the characteristic) and Rule 4 (search for the interval with the maximum characteristic).

The new rule for calculating the characteristic $R(i)$ of the interval $(x_{i-1}, x_i)$ will consist of the following operations:
\begin{itemize}
\item
Calculate the value $R_{glob}(i)$ corresponding to the larger estimate of the Lipschitz constant
\[
R_{glob}(i)=\Delta_i+\frac{(z_i-z_{i-1})^2}{r_{glob}^2\mu^2\Delta_i}-2\frac{z_i+z_{i-1}-2z^*}{r_{glob}\mu}.
\]
\item
Calculate the value $R_{loc}(i)$ corresponding to the smaller estimate of the Lipschitz constant
\[
R_{loc}(i)=\Delta_i+\frac{(z_i-z_{i-1})^2}{r_{loc}^2\mu^2\Delta_i}-2\frac{z_i+z_{i-1}-2z^*}{r_{loc}\mu}.
\]
\item
Determine the characteristic $R(i)$ as
\begin{equation}\label{pho}
R(i) = \max\{\rho R_{loc}(i),R_{glob}(i)\}, \textrm{where} \; \rho = \left(\frac{1-1/r_{glob}}{1-1/r_{loc}}\right)^2,
\end{equation}   
\end{itemize}

%Russian
The new rules for finding the interval with the maximum characteristic will be as follows:
\begin{itemize}
\item 
Select the interval $(x_{t-1},x_t)$ corresponding to the maximum characteristic
\[
R(t)= \max_{1 \leq i \leq k}R(i).
\]
\item
Fix the value $r = r_{loc}$ if $\rho R_{loc}(t) > R_{glob}(t)$, otherwise fix $r=r_{glob}$.
\item
Use this value of $r$ in Rule 5 of the algorithm in the computing of the next trial point.
\end{itemize}

This method for computing the characteristic is substantiated as follows. 
%Russian
Each search iteration will yield an interval with the current minimum value $z^*$ from (\ref{z}) at one of its boundaries. In the final phase of the search, this interval will correspond to the interval containing the global minimum, i.e. it will be the best one in terms of conducting further trials within it.

Let the current minimum value of $z^*$ from (\ref{z}) be achieved at the left point of the $i^{\rm th}$ interval, i.e. $z^* = z_{i-1}$. 
As proven in \cite{Strongin2000}, according to the rule (\ref{R}) the following inequality will be true: 
\[
R(i) \geq \Delta_i \left( 1 - \frac{1}{r} \right)^2.
\]
Therefore, for evaluating the characteristics $R_{loc}(i)$ and $R_{glob}(i)$ calculated with different parameters $r_{loc}$ and $r_{glob}$, the following relation will hold:
\[
	\Delta_i \left( 1 - \frac{1}{r_{glob}} \right)^2 > \Delta_i \left( 1 - \frac{1}{r_{loc}} \right)^2.
\]

Thus, when choosing the largest of the characteristics in accordance with
\[
R(i) = \max\{R_{loc}(i),R_{glob}(i)\}
\]
%as a rule,
the characteristic $R_{glob}(i)$ corresponding to the higher estimate of the Lipschitz constant will be chosen; the lower estimate (which speeds up the process of refining the current solution) will not be used.
However, if we multiply the lower estimate for the characteristic $R_{loc}(i)$ by the coefficient $\rho$ in accordance with (\ref{pho}),then such lower estimates will be equal, 
thus the choice of the characteristic $R_{loc}(i)$ corresponding to the lower estimate of the Lipschitz constant will become more likely.

@@

%Russian
A numerical comparison of the algorithms was carried out by solving several series of problems generated by the GKLS generator \cite{Gaviano2003}. This generator of multiextremal functions is widely used to compare global optimization methods (see, for example, \cite{Barkalov2018,Paulavicius2014,Sergeyev2015}). In this study, six series each containing 100 problems of dimensions $N = 3,4,5$ were solved. For each dimension, \textit{Simple} and \textit{Hard} problems were generated, differing in the size of the attraction region for local extremums and global extremum.
The problem was considered solved if the method conducted the next trial in sequence at a point that was in the $\delta$-neighborhood of the global minimizer $y^\ast$, 
i.e. $\left\|y^k-y^\ast\right\| <\delta\left\|b-a\right\|$, where  $a$ and $b$ are the boundaries of the search domain $D$.

@@

The averaged numbers of iterations performed by the algorithms are presented in Table \ref{tab:1}.
For the GSA method the values of the parameter $r=4.8$ when solving the problems of the \textit{Simple} class and $r=5.6$ when solving the problems of the \textit{Hard} class were used. 
These values are the minimum ones (with the accuracy 0.1), at which all problems have been solved successfully.
When solving the problems from the above classes by the GSA-DL method, the value of the parameter $r$ specified above was selected for the upper estimate of the Lipschitz constant, i.e. the value $r_{glob} = r$ was set, which was complemented by the values $r_{loc}=1.8$, $r_{loc}=2.1$ and $r_{loc}=2.4$. 
The number of unsolved problems is specified in brackets.

@@

The advantages of the GSA-DL algorithm over its prototype are also confirmed by the operational characteristics of the algorithms as well.

@@

The operational characteristics for the GSA and GSA-DL methods obtained when solving the \textit{Simple} and \textit{Hard} problem series with the dimensionalities $N=4$ and $N=5$ are presented in Fig. \ref{oper4} and Fig. \ref{oper5}, respectively. The values of the parameters $r$ used for estimating the Lipschitz constant are given in the figures.

The lower curves in Fig. \ref{oper4} and Fig. \ref{oper5} feature the characteristics of GSA whereas the upper ones, those of the GSA-DL. Such relative positions of the curves show the algorithm with two estimates of the Lipschitz constant is much faster on average when solving the problem series than the algorithm using a single estimate of the constant.
%Russian
Note that to solve problems of all classes (except for the \textit{Hard} class at $N=5$) the GSA-DL method requires about half as many trials as the GSA. The deterioration of the results in the case of the \textit{Hard} class at $N=5$ is explained by the complexity of this class' functions, which have a large attraction region of local minima and a narrow attraction region of the global minimum. To correctly solve such problems, the GSA-DL method often uses a higher estimate of the Lipschitz constant, thus reducing the speed difference of the GSA and GSA-DL algorithms.
